LAGOS lake depth

### 2020-04-29 README.Rmd
title grammar
point to combined figs and appendix

## Bathymetry data from thousands of lakes show that difficulty modeling in-lake slope confounds lake depth prediction

@@

Figures: [manuscript/figures.pdf](manuscript/figures.pdf)

>>>>

## Bathymetry data from thousands of lakes show that lake depth prediction is confounded by difficulty modeling inlake slope

@@

Figures: [manuscript/figures.pdf](manuscript/combined.pdf)
